\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter
%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Kenil Mavani}
\newcommand{\yourWebsite}{}
\newcommand{\yourEmail}{kenilmavani68@gmail.com}
\newcommand{\yourPhone}{9726134456}
\newcommand{\hackerearthUserName}{@kenil1}
\newcommand{\linkedInUserName}{kenil-mavani}

% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsite}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsite}{abdullaharif.tech}
%     \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape \yourName} \\ \vspace{1pt}
    \small \yourPhone $|$ \href{mailto:\yourEmail}{\underline{\yourEmail}} $|$ 
    \href{https://linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://hackerearth.com/\hackerearthUserName}{\underline{hackerearth/\hackerearthUserName}}
\end{center}

%--------------------------------------------------------------
%     GOAL
%--------------------------------------------------------------
\section{Goal}
    Being enthusiastic coder I enjoy to explore and learn the new and upcoming technologies. I thus wish to serve in your esteemed organization and witness the growth of organization along with myself growth.\\
\sectionsep

\hspace{1cm}

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Supertax}{Software Development Engineer}{Mumbai, IN}{Jun 2019 – present}
\begin{tightemize}
    \item Working on JAVA \textbf{spring boot} application.
    %  \item Here is another bullet that I might choose to uncomment for some jobs
    \item Providing end-to-end solutions, Solving complex problems, architecture, design, and development tasks, Designed and implemented data storage solutions, Designed new features and services to support client applications with use of Multi-threading, Hibernate, Redis, Rest API, Java, ReactJS, Maven, Flyway, MySql, Linux, Jenkins, GIT.
    \item Setup a CI/CD pipeline and exceeded requirements in each stage, which lead to the application being pushed to production.
\end{tightemize}
\sectionsep

\resumeHeading{Square Infosoft}{Software Trainee}{Surat,In}{May 2018 - July 2018}
\begin{tightemize}
    \item Developed design for Railway ticket booking system \textbf{(ConfirmTicket)} in SWIFT.
\end{tightemize}
\sectionsep
\sectionsep

\hspace{1cm}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Swap degree and school if your school is reputable
\educationHeading{B.E in Computer Engineering }{Saravjanik College of Engineering and Technology (7.4/10 CGPA)}{Surat, IN}{May 2019}

% \courseWork{Data Structures and Algorithms; Operating Systems;  Computer Security; Software Testing; Advanced Networking; Big Data Analytics}
\sectionsep

\hspace{1cm}

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\Project{DIGI - LYCEUM}{https://github.com/kenilmavani/navigation}
\descript{Unity,Vuforia,Ionic}\\
We incorporated AR into indoor positioning and designed a novel user interface with a compelling application that delivers an interactive indoor navigation experience through AR graphical views aligned with indoor objects.\\
\sectionsep
  
\Project{ChatBot}{https://github.com/kenilmavani/chatadmin}
\descript{Python, Dialogflow, Ngrok}\hfill \\
I created a chat bot for Admin process inquires for students.They can use it on their google assistant by saying hello admin.\\
\sectionsep

\Project{E-HelthCard}{}
\descript{PHP,CSS,HTML,MYSQL}\hfill \\
Smart Health card is a digital healthcare solution it uses cloud EHR(Electronic Health
Record) technology, by providing users the power to carry their health records in
portable, user friendly and secure manner. It saves time for patient and for providers
that avoids unnecessary delays and tests while protecting patients private
information. The vital part is that it could be accessed in case of travel, emergency or
routine medical visit. It consists Medical records like PATH Lab Tests, Blood Reports,
Prescriptions, X-Ray, C.T. Scan, Sonography Reports, Bone Marrow Profile, Allergy
Tests etc.
\sectionsep

\Project{Hotel Management System}{}
\descript{JAVA,servlet,HTML,MYSQL}\hfill \\
A program that authenticates users based on their typing patterns. And a spoofer that uses the genetic algorithm to mimic the user's typing pattern.
\sectionsep

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{resumeSkillList}
    \singleItem{Languages:}{Java8, C++, Python, PHP, Bash, C, SQL}
    \\
    \singleItem{Web Development:}{HTML/CSS}
    \\
    \singleItem{Technology:}{Git, AWS, Docker, Apache,DBMS,Spring Boot,MVC,CI/CD,Devops}
\end{resumeSkillList}

 % A more concise alternate 
% \begin{resumeSkillList}
%     \doubleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket}%
%     {Databases:}{SQL, MongoDB, Neo4j, DynamoDB}
%     \\
%     \doubleItem{Web Development:}{JavaScript, TypeScript, React, HTML/CSS}
%     {Technology:}{Git, AWS, GCP, Azure, Docker, \LaTeX}%
% \end{resumeSkillList}
\end{document}